Learning and comparing functional connectomes across subjects

### 2013-02-21 paper.tex
Fix the citation ordering
Cleanup before addressing reviews

@@

% General introduction
Functional connectivity reveals the synchronization of distant neural systems
via correlations in neurophysiological measures of brain activity 
\cite{friston1993, biswal1995}.  Given that
high-level function emerges from the interaction of specialized units
\cite{tononi1992},
functional connectivity is an essential part of the description of brain
function, that complements the localizationist picture emerging from the
systematic mapping of regions recruited in tasks\cite{sporns2004}. However,
while there exists a well-defined standard analysis framework for activation
mapping that enables statistically-controlled comparisons across subjects
\cite{friston1995}, group-level analyses of functional connectivity still face
many open methodological challenges. Deriving a picture of a single subject's
functional connectivity is by itself not straightforward, as the brain comprises
a myriad of interacting subsystems and its connectivity must be decomposed into
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary view is
that of connections linking localized functional modules depicted as a graph
\cite{bullmore2009}. This representation of brain connectivity is often called
the functional connectome \cite{sporns2005} and is the focus of intense
worldwide research efforts as it holds promises of new insights in cognition and
pathologies \cite{greicius2008b,biswal2010,fox2010}.

@@

%% XXX number of regions
% CAMERON added this since it was left to do, I don't know if it really says
% anything 
\paragraph{Optimal number of regions}
%
Defining an optimal number of regions to use for whole-brain connectivity analysis bears
careful consideration. On one hand we desire a sufficiently large number of
regions to guarantee that they are functionally homogeneous regions and adequately 
represent the connectivity information present in the data. On the other hand
too many regions will render statistical inference challenging, 
result in an explosion in computational complexity,
and interfere with the interpretability of observed connections. For functional
parcellation, cross-validation methods can be employed to estimate an optimal 
number of regions based on homogeneity, the ability to reproduce 
connectivity information present at the voxel scale, and the ability to
obtain the same parcellations from independent data 
\cite{craddock2012, blumensath2012}. In general these metrics do not result in an
obvious peak at a ``best'' number of regions, but instead offer a range over
which the number of regions can be chosen based on the needs of the analysis at
hand.

@@

% XXX: need to give details on the dataset used here

@@

% XXX: must comment on the estimator figure

@@

% XXX: where to insert this in the above paragraph: cite the
% Fransson/Marrelec paper on the role of the PCC

@@

{
%\clearpage
\section*{References} \small \bibliographystyle{elsarticle-num-names}
\bibliography{biblio} }

>>>>

\biboptions{sort}

@@

% General introduction
Functional connectivity reveals the synchronization of distant neural systems
via correlations in neurophysiological measures of brain activity 
\cite{friston1993, biswal1995}.  Given that
high-level function emerges from the interaction of specialized units
\cite{tononi1992},
functional connectivity is an essential part of the description of brain
function, that complements the localizationist picture emerging from the
systematic mapping of regions recruited in tasks \cite{sporns2004}. However,
while there exists a well-defined standard analysis framework for activation
mapping that enables statistically-controlled comparisons across subjects
\cite{friston1995}, group-level analyses of functional connectivity still face
many open methodological challenges. Deriving a picture of a single subject's
functional connectivity is by itself not straightforward, as the brain comprises
a myriad of interacting subsystems and its connectivity must be decomposed into
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary view is
that of connections linking localized functional modules depicted as a graph
\cite{bullmore2009}. This representation of brain connectivity is often called
the functional connectome \cite{sporns2005} and is the focus of intense
worldwide research efforts as it holds promises of new insights in cognition and
pathologies \cite{greicius2008b,biswal2010,fox2010}.

@@

\paragraph{Optimal number of regions}
%
Defining an optimal number of regions to use for whole-brain connectivity analysis bears
careful consideration. On one hand we desire a sufficiently large number of
regions to guarantee that they are functionally homogeneous regions and adequately 
represent the connectivity information present in the data. On the other hand
too many regions will render statistical inference challenging, 
result in an explosion in computational complexity,
and interfere with the interpretability of observed connections. For functional
parcellation, cross-validation methods can be employed to estimate an optimal 
number of regions based on homogeneity, the ability to reproduce 
connectivity information present at the voxel scale, and the ability to
obtain the same parcellations from independent data 
\cite{craddock2012, blumensath2012}. In general these metrics do not result in an
obvious peak at a ``best'' number of regions, but instead offer a range over
which the number of regions can be chosen based on the needs of the analysis at
hand.

@@

@@

@@

@@

{
%\clearpage
\section*{References}
\small
%\bibliographystyle{elsarticle-num-names}
\bibliographystyle{model1b-num-names}
\bibliography{biblio} }
